### 2014-03-01 paper/extensions.tex
Examples
Signed-off-by: Edward Z. Yang <ezyang@cs.stanford.edu>
points
scheduling policies

\section{Extensions to the IFC language}
\label{sec:extensions}
\cut{

}

\subsection{Type safety}

@@

>>>>

\section{Extensions and Limitations}
\label{sec:extensions}

In this section we consider several extensions to our IFC system.
%
Specifically, we discuss how the specification language can be
extended to consider other IFC-aware features (e.g., fine-grained
labeled values), a static type system, or more complex scheduling
policies.
%
When considering these extensions we also highlight some limitations
of our approach.

\subsection{IFC-aware language features}
\label{sec:extensions:labeled}

\subsubsection{Labeled objects}

\paragraph{Labeled values}
\paragraph{Labeled references}
\paragraph{Labeled synchronization primitives}
\subsubsection{Privileges}
\subsubsection{Clearance}

\subsection{Type safety}
\label{sec:extensions:types}

@@

\subsection{Safe scheduling policies}
Our specification language is parametrized by a scheduling policy
|alpha|, which maps a task list to a potentially different task list.
%
As previously discussed, the precise definition of |alpha|
dictates whether the language is TSNI, TINI, or neither.
%
For simplicity we considered two popular policies |roundrobinf| and
|seqf| for which we showed TSNI and TINI, respectively.
%
However, our definitions allow for other scheduling policies that only
rely on the current task list.
%
For example, this allows us to implement the scheduler of~\tocite{}
that always schedules less sensitive threads first; this can be
employed to address external timing covert channels where an attacker
can measure the delay between output events.\footnote{
  When considering a label lattice that is not totally ordered, e.g.,
  DCLabels~\tocite{}, this scheduling policy is considerably more
  complex. See~\tocite{}.
}
%
More generally, we belove that deterministic schedulers that always
make ``low-progress,'' i.e., if a task whose label is not above the
current task's label will will eventually run, and do not decide which
low tasks to schedule according to data more sensitive than the tasks'
label, i.e., the scheduler does not schedule one public thread over
another according to sensitive data, to be safe.
%
We leave the proof of this claim to future work.
%

Despite allowing a number of practical schedulers to be expressed, our
scheduler parametrization is limited.
%
For instance, since |alpha| is a map on task lists, schedulers
that rely on the global state |iS|, or previous task configurations
cannot be expressed.
%
Though, we do not belove this to be a fundamental limitation, our
current formalization cannot directly be applied to more-powerful, but
safe, scheduling policies, as considered in~\tocite{}.

\subsection{Other target languages}

\subsubsection{External effects}
\label{sec:extensions:external}
Application specific, use XHR as driving example.
General way to think of safety is internalize and treat as a labeled
object; or message to thread that has access to unsafe API, but
exposes labeled safe messaging API.

\cut{

}
\begin{itemize}
\item Label transition systems.
\item Non-deterministic reduction.
\end{itemize}
